PubCrawl: A Publication Search Engine

### 2012-05-18 report/paper.tex
Edit abstract for conciseness
Fix date
Cosmetic changes
Use a nicer font

Fix "overfull hbox" warning

Reformat some BibTeX entries
Introduce notation for containing component

\documentclass[12pt]{article}
\setcounter{secnumdepth}{2} 
\title{PubCrawl: A Publication Search Engine}
\author{Frank Li (frankli@mit.edu) \\
Abhishek Sarkar (aksarkar@mit.edu)\\
Manasi Vartak (mvartak@mit.edu)}
\date{May 16, 2012}

\usepackage{graphicx}
\usepackage[letterpaper,margin=1in]{geometry}

@@

There are several existing search engines for academic papers, most prominently
Google Scholar, \citeseer, and Microsoft Academic Search. Google Scholar uses a
proprietary algorithm which combines several approaches. However, researchers
have partially reverse engineered it \cite{beel09a, beel09b}. In particular,
the algorithm is biased towards highly cited papers, which should highly rank
important papers in the standard literature. However, the bias
will also make the algorithm miss more recent influential papers. Researchers
also uncovered several weaknesses in Google's automatic processing of documents
which could allow authors to game search rankings \cite{beel10}.

@@

\begin{figure}[bt]
  \begin{center}
    \includegraphics[width=8in]{images/interface}
  \end{center}
  \caption{PubCrawl user interface}
  \label{interface}
\end{figure}

@@

\begin{equation}
R(p)= n\left(\frac{1 - d}{N} + d\left(\sum_{c \in C}
\frac{R(c)}{D(c)}+E(p)\right)\right)
\end{equation}

where $R(\cdot)$ is the PageRank of a node, $D(\cdot)$ is the outdegree of a
node, $E(\cdot)$ is the score source of a node (needed to converge with
cycles), $d$ is the damping factor, and $n$ is the normalizing factor.

@@

We found initializing the PageRank of each paper to a constant gave suboptimal
results because the ACM citation graph has a high number of small components.
Papers in these components end with disproportionately high PageRank because
further iterations do not change their initial value very much. Instead, we set
the initial value of a paper's PageRank to the proportion of all papers
contained in its component.

>>>>

\documentclass[12pt]{article}
\setcounter{secnumdepth}{2} 
\title{PubCrawl: A Publication Search Engine}
\author{Frank Li (frankli@mit.edu) \\
Abhishek Sarkar (aksarkar@mit.edu)\\
Manasi Vartak (mvartak@mit.edu)}

\usepackage{graphicx}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{palatino}
\usepackage{mathpazo}

@@

There are several prominent search engines for academic papers: Google Scholar,
\citeseer, and Microsoft Academic Search. Google Scholar uses a proprietary
algorithm which combines several approaches. However, researchers have
partially reverse engineered it \cite{beel09a, beel09b}. In particular, the
algorithm is biased towards highly cited papers, which should highly rank
important papers in the standard literature. However, the bias will also make
the algorithm miss more recent influential papers. Researchers also uncovered
several weaknesses in Google's automatic processing of documents which could
allow authors to game search rankings \cite{beel10}.

@@

\begin{figure}[bt]
  \begin{center}
    \includegraphics[width=\textwidth]{images/interface}
  \end{center}
  \caption{PubCrawl user interface}
  \label{interface}
\end{figure}

@@

\begin{equation}
R(p)= n\left(\frac{1 - d}{N} + d\left(\sum_{c \in C(p)}
\frac{R(c)}{D(c)}+E(p)\right)\right)
\end{equation}

where $R(\cdot)$ is the PageRank of a node, $D(\cdot)$ is the outdegree of a
node, $E(\cdot)$ is the score source of a node (needed to converge with
cycles), $C(\cdot)$ is the component containing a node, $d$ is the damping
factor, and $n$ is the normalizing factor.

@@

We found initializing the PageRank of each paper to a constant gave suboptimal
results because the ACM citation graph has a high number of small components.
Papers in these components end with disproportionately high PageRank because
further iterations do not change their initial value very much. Instead, we set
the initial value of a paper's PageRank to $\vert C(p) \vert / N$ or the
proportion of all papers contained in its component.
